---
title: "Analysis 'Projektarbeit 2017'"
output:
  pdf_document: default
  html_notebook: default
---

# # Clearing work enviroment, setting libraries and constants
```{r}
rm(list=ls())

library(tidyverse)


pathMEM <- "C:/Users/jog54yy/Documents/Projektarbeit_SS2017/Data/Memory/"
pathET <- "C:/Users/jog54yy/Documents/Projektarbeit_SS2017/Data/prot/"

```



# # Reading eye tracking data in 
```{r}
options(warn=0)  # 2=Turn warnings into errors / 0=default

# ALL DATA
vpn <- paste("vpja",ifelse(c(1:78,81:96)<10,"0",""),c(1:78,81:96),sep="")
bed <- rep(c("free","mem"),47)

# ORIGINALLY ACQUIRED DATA
#vpn <- paste("vpja",ifelse(c(1:78)<10,"0",""),c(1:78),sep="")
#bed <- rep(c("free","mem"),39)

bed <- bed[!(vpn %in% "vpja23")]  # Daten fehlen
vpn <- vpn[!(vpn %in% "vpja23")]  

# Loop over subjects
erg <- numeric(); nvalid <- numeric(); cleantime <- numeric()
for (vp in vpn) {
  #  print(vp)
  
  prot <- read.csv2(paste(pathET,vp,"_Fixations.csv",sep=""))
  
  # Restrict to trials with valid baseline?
  nvalid <- c(nvalid,sum(prot$blok==1))
  prot <- prot[prot$blok==1,]
  
  cleantime <- c(cleantime,mean(prot$cleantime))
  
  erg <- rbind(erg,apply(prot[,8:ncol(prot)],2,mean,na.rm=TRUE))
}

et.dfw <- data.frame(code=vpn,group=bed,nvalid,cleantime,erg) 
  

et.dfl <- gather(et.dfw, key, value, fix.face:sac.bnongaze, factor_key=TRUE) %>% 
  mutate(
    key = as.character(key),
    fixations =
      as.factor(
        ifelse(startsWith(key, "fix."), "fix",
             ifelse(startsWith(key, "fixn."), "fixn",
                    ifelse(startsWith(key, "fixlat."), "fixlat",NA)))),
    region = 
      as.factor(
        ifelse(endsWith(key, ".face"), "face",
               ifelse(endsWith(key, ".body"), "body",
                      ifelse(endsWith(key, ".gaze"), "gaze",
                             ifelse(endsWith(key, ".nongaze"), "nongaze", NA))))),
    saccades = as.factor(
      ifelse(endsWith(key, ".pgaze"), "pgaze",
             ifelse(endsWith(key, ".fgaze"), "fgaze",
                    ifelse(endsWith(key, ".bgaze"), "bgaze",
                           ifelse(endsWith(key, ".pnongaze"), "pnongaze",
                                  ifelse(endsWith(key, ".fnongaze"), "fnongaze",
                                         ifelse(endsWith(key, ".bnongaze"), "bnongaze", NA)))))))) %>% 
  arrange(code)

rm(prot, bed, cleantime, nvalid, vp, vpn, erg)
```



# # Reading memory data in
```{r}

# ALL DATA
vpn <- paste("vpja",ifelse(c(1:78,81:96)<10,"0",""),c(1:78,81:96),sep="")
bed <- rep(c("free","mem"),47)

# ORIGINALLY ACQUIRED DATA
#vpn <- paste("vpja",ifelse(c(1:78)<10,"0",""),c(1:78),sep="")
#bed <- rep(c("free","mem"),39)

# Loop over subjects
erg <- numeric()
for (vp in vpn) {
  # print(vp)
  
  prot <- read.csv2(paste(pathMEM,vp,".csv",sep=""))
  
  # Item recalled
  gaze <- sum(prot$memgazedat)
  nogaze <- sum(prot$memnongazedat)
  
  erg <- rbind(erg,c(gaze,nogaze))
}

mem.dfw <- data.frame(code=vpn,bed,erg)               
names(mem.dfw) <- c("code","bed","memgaze","memnogaze")

rm(gaze, nogaze, erg, prot, bed, vp, vpn)
```



# # Combinig eye tracking and memory data?!?!
```{r}



```

```{python}
print 'Hello World!'
```





# # Plots by Matthias 
```{r}
####################################################
# Plots: Fixation data
x11()
par(mfrow=c(2,3))

farben <- c("green","red","blue","yellow")

for (st in seq(5,16,4)) {
  # Fixation density
  m  <- cbind(apply(et.dfw[et.dfw$group=="free",st:(st+3)],2,mean),
              apply(et.dfw[et.dfw$group=="mem",st:(st+3)],2,mean))
  se <- cbind(apply(et.dfw[et.dfw$group=="free",st:(st+3)],2,sd)/sqrt(sum(et.dfw$group=="free")),
              apply(et.dfw[et.dfw$group=="mem",st:(st+3)],2,sd)/sqrt(sum(et.dfw$group=="mem")))

  yrng <- c(0,max(m+se))
  
  x <- barplot(m,beside=TRUE,col=farben,ylim=yrng,xlab="",ylab="% of total fixation time")
  arrows(x,m-se,x,m+se,length=0.03,angle=90,code=3,col="black")
  axis(1,apply(x,2,mean),c("Free viewing","Explicit encoding"),tick=FALSE)
}

legend(max(x),max(yrng),c("Face","Body","Cued","Uncued"),fill=farben,xjust=1,yjust=1)

# Plots: Saccade data
farben <- c("blue","yellow")
ttxt <- c("Person","Face","Body")

for (i in 1:3) {
  st <- (17:19)[i]
  
  # Fixation density
  m  <- cbind(apply(et.dfw[et.dfw$group=="free",c(st,st+3)],2,mean),
              apply(et.dfw[et.dfw$group=="mem",c(st,st+3)],2,mean))
  se <- cbind(apply(et.dfw[et.dfw$group=="free",c(st,st+3)],2,sd)/sqrt(sum(et.dfw$group=="free")),
              apply(et.dfw[et.dfw$group=="mem",c(st,st+3)],2,sd)/sqrt(sum(et.dfw$group=="mem")))
  
  yrng <- c(0,max(m+se))
  
  x <- barplot(m,beside=TRUE,col=farben,ylim=yrng,xlab="",ylab="% of total fixation time")
  arrows(x,m-se,x,m+se,length=0.03,angle=90,code=3,col="black")
  axis(1,apply(x,2,mean),c("Free viewing","Explicit encoding"),tick=FALSE)
  
  title(ttxt[i])
}

legend(max(x),max(yrng),c("Cued","Uncued"),fill=farben,xjust=1,yjust=1)
```


# # Anova by Matthias
```{r}
require("car")

# Fixations Face + Body in Free Viewing vs. Explicit Encoding
ergtab <- numeric()
for (st in seq(5,16,4)) {
  msd <- c(mean(et.dfw[et.dfw$group=="free",st]),sd(et.dfw[et.dfw$group=="free",st]),
           mean(et.dfw[et.dfw$group=="mem",st]),sd(et.dfw[et.dfw$group=="mem",st]))
  teststat <- t.test(et.dfw[,st] ~ et.dfw$group)
  
  ergtab <- rbind(ergtab,c(msd,teststat$parameter,teststat$statistic,teststat$p.value))
}

colnames(ergtab) <- c("M(free)","SD(free)","M(mem)","SD(mem)","df","t","p")
print(ergtab)

# ANOVA Fixations characteristics
# 2 (Group) x 2 (Gaze) ANOVA
icond <- gl(2,1,labels=c("cued","uncued"))
idata <- data.frame(icond)

for (st in seq(7,16,4)) {
  carmod <- lm(as.matrix(et.dfw[,st:(st+1)]) ~ et.dfw$group)
  print(Anova(carmod, idata=idata, idesign=~icond, type="III"))
}

# ANOVA Saccades
# 2 (Group) x 2 (Gaze) ANOVA
for (st in 17:19) {
  carmod <- lm(as.matrix(et.dfw[,c(st,st+3)]) ~ et.dfw$group)
  print(Anova(carmod, idata=idata, idesign=~icond, type="III"))
}

```






Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).







