---
title: "Analysis 'Projektarbeit 2017'"
---

# # Clearing work enviroment, setting libraries and constants
```{r}
rm(list=ls())

library(tidyverse)

pathMEM <- "data/Memory/"
pathET <- "data/prot/"
pathFB <- "data/FB/"

```



# # Reading eye tracking data in 
```{r}
options(warn=0)  # 2=Turn warnings into errors / 0=default

# ALL DATA
vpn <- paste("vpja",ifelse(c(1:78,81:96)<10,"0",""),c(1:78,81:96),sep="")
bed <- rep(c("free","mem"),47)

# ORIGINALLY ACQUIRED DATA
#vpn <- paste("vpja",ifelse(c(1:78)<10,"0",""),c(1:78),sep="")
#bed <- rep(c("free","mem"),39)

bed <- bed[!(vpn %in% "vpja23")]  # Daten fehlen
vpn <- vpn[!(vpn %in% "vpja23")]  

# Loop over subjects
erg <- numeric(); nvalid <- numeric(); cleantime <- numeric()
for (vp in vpn) {
  #  print(vp)
  
  prot <- read.csv2(paste(pathET,vp,"_Fixations.csv",sep=""))
  
  # Restrict to trials with valid baseline?
  nvalid <- c(nvalid,sum(prot$blok==1))
  prot <- prot[prot$blok==1,]
  
  cleantime <- c(cleantime,mean(prot$cleantime))
  
  erg <- rbind(erg,apply(prot[,8:ncol(prot)],2,mean,na.rm=TRUE))
}

et.dfw <- data.frame(code=vpn,group=bed,nvalid,cleantime,erg) 
  

et.dfl <- gather(et.dfw, key, value, fix.face:sac.bnongaze, factor_key=TRUE) %>% 
  mutate(
    key = as.character(key),
    fixations =
      as.factor(
        ifelse(startsWith(key, "fix."), "fix",
             ifelse(startsWith(key, "fixn."), "fixn",
                    ifelse(startsWith(key, "fixlat."), "fixlat",NA)))),
    region = 
      as.factor(
        ifelse(endsWith(key, ".face"), "face",
               ifelse(endsWith(key, ".body"), "body",
                      ifelse(endsWith(key, ".gaze"), "gaze",
                             ifelse(endsWith(key, ".nongaze"), "nongaze", NA))))),
    saccades = as.factor(
      ifelse(endsWith(key, ".pgaze"), "pgaze",
             ifelse(endsWith(key, ".fgaze"), "fgaze",
                    ifelse(endsWith(key, ".bgaze"), "bgaze",
                           ifelse(endsWith(key, ".pnongaze"), "pnongaze",
                                  ifelse(endsWith(key, ".fnongaze"), "fnongaze",
                                         ifelse(endsWith(key, ".bnongaze"), "bnongaze", NA)))))))) %>% 
  arrange(code)

rm(prot, bed, cleantime, nvalid, vp, vpn, erg)
```



# # Reading memory data in
```{r}

# ALL DATA
vpn <- paste("vpja",ifelse(c(1:78,81:96)<10,"0",""),c(1:78,81:96),sep="")
bed <- rep(c("free","mem"),47)

# ORIGINALLY ACQUIRED DATA
#vpn <- paste("vpja",ifelse(c(1:78)<10,"0",""),c(1:78),sep="")
#bed <- rep(c("free","mem"),39)

# Loop over subjects
erg <- numeric()
for (vp in vpn) {
  # print(vp)
  
  prot <- read.csv2(paste(pathMEM,vp,".csv",sep=""))
  
  # Item recalled
  gaze <- sum(prot$memgazedat)
  nogaze <- sum(prot$memnongazedat)
  
  erg <- rbind(erg,c(gaze,nogaze))
}

mem.dfw <- data.frame(code=vpn,bed,erg)               
names(mem.dfw) <- c("code","bed","memgaze","memnogaze")

rm(gaze, nogaze, erg, prot, bed, vp, vpn)
```



# # Reading questionnaire data in
```{r}

demo.dfw <- read_csv2(paste(pathFB,"Projektarbeit_Dateneingabemaske.csv", sep="")) %>% 
  transmute(
    vp = as.factor(VP_Nr),
    sex = as.factor(Demo_Sex),
    age = Demo_Alter,
    aq_social = ifelse((5-AQK_1) < 3, 1, 0) + ifelse((5-AQK_7) < 3, 1, 0) + ifelse(AQK_8 < 3, 1, 0) + ifelse((5-AQK_10) < 3, 1, 0) + ifelse((5-AQK_11) < 3, 1, 0) + ifelse(AQK_13 < 3, 1, 0) + ifelse((5-AQK_14) < 3, 1, 0) + ifelse((5-AQK_20) < 3, 1, 0) + ifelse((5-AQK_24) < 3, 1, 0) + ifelse((5-AQK_28) < 3, 1, 0) + ifelse((5-AQK_31) < 3, 1, 0), # 5- 'item' for reversed items, then if 1/2 -> 1, 3/4 -> 0  
    aq_imagination = ifelse((5-AQK_3) < 3, 1, 0) + ifelse((5-AQK_5) < 3, 1, 0) + ifelse((5-AQK_6) < 3, 1, 0) + ifelse((5-AQK_9) < 3, 1, 0) + ifelse((5-AQK_16) < 3, 1, 0) + ifelse((5-AQK_17) < 3, 1, 0) + ifelse((5-AQK_18) < 3, 1, 0) + ifelse((5-AQK_22) < 3, 1, 0) + ifelse((5-AQK_23) < 3, 1, 0) + ifelse((5-AQK_26) < 3, 1, 0) + ifelse((5-AQK_32) < 3, 1, 0) + ifelse((5-AQK_33) < 3, 1, 0),
    aq_communication = ifelse(AQK_2 < 3, 1, 0) + ifelse(AQK_4 < 3, 1, 0) + ifelse(AQK_12 < 3, 1, 0) + ifelse(AQK_15 < 3, 1, 0) + ifelse(AQK_19 < 3, 1, 0) + ifelse(AQK_21 < 3, 1, 0) + ifelse(AQK_25 < 3, 1, 0) + ifelse(AQK_27 < 3, 1, 0) + ifelse(AQK_29 < 3, 1, 0) + ifelse(AQK_30 < 3, 1, 0),
    aq_sumscore = ifelse((5-AQK_1) < 3, 1, 0) + ifelse(AQK_2 < 3, 1, 0) + ifelse((5-AQK_3) < 3, 1, 0) + ifelse(AQK_4 < 3, 1, 0) + ifelse((5-AQK_5) < 3, 1, 0) + ifelse((5-AQK_6) < 3, 1, 0) + ifelse((5-AQK_7) < 3, 1, 0) + ifelse(AQK_8 < 3, 1, 0) + ifelse((5-AQK_9) < 3, 1, 0) + ifelse((5-AQK_10) < 3, 1, 0) + ifelse((5-AQK_11) < 3, 1, 0) + ifelse(AQK_12 < 3, 1, 0) + ifelse(AQK_13 < 3, 1, 0) + ifelse((5-AQK_14) < 3, 1, 0) + ifelse(AQK_15 < 3, 1, 0) + ifelse((5-AQK_16) < 3, 1, 0) + ifelse((5-AQK_17) < 3, 1, 0) + ifelse((5-AQK_18) < 3, 1, 0) + ifelse(AQK_19 < 3, 1, 0) + ifelse((5-AQK_20) < 3, 1, 0) + ifelse(AQK_21 < 3, 1, 0) + ifelse((5-AQK_22) < 3, 1, 0) + ifelse((5-AQK_23) < 3, 1, 0) + ifelse((5-AQK_24) < 3, 1, 0) + ifelse(AQK_25 < 3, 1, 0) + ifelse((5-AQK_26) < 3, 1, 0) + ifelse(AQK_27 < 3, 1, 0) + ifelse((5-AQK_28) < 3, 1, 0) + ifelse(AQK_29 < 3, 1, 0) + ifelse(AQK_30 < 3, 1, 0) + ifelse((5-AQK_31) < 3, 1, 0) + ifelse((5-AQK_32) < 3, 1, 0) + ifelse((5-AQK_33) < 3, 1, 0))

```



# # Plots by Matthias 
```{r}
####################################################
# Plots: Fixation data
x11()
par(mfrow=c(2,3))

farben <- c("green","red","blue","yellow")

for (st in seq(5,16,4)) {
  # Fixation density
  m  <- cbind(apply(et.dfw[et.dfw$group=="free",st:(st+3)],2,mean),
              apply(et.dfw[et.dfw$group=="mem",st:(st+3)],2,mean))
  se <- cbind(apply(et.dfw[et.dfw$group=="free",st:(st+3)],2,sd)/sqrt(sum(et.dfw$group=="free")),
              apply(et.dfw[et.dfw$group=="mem",st:(st+3)],2,sd)/sqrt(sum(et.dfw$group=="mem")))

  yrng <- c(0,max(m+se))
  
  x <- barplot(m,beside=TRUE,col=farben,ylim=yrng,xlab="",ylab="% of total fixation time")
  arrows(x,m-se,x,m+se,length=0.03,angle=90,code=3,col="black")
  axis(1,apply(x,2,mean),c("Free viewing","Explicit encoding"),tick=FALSE)
}

legend(max(x),max(yrng),c("Face","Body","Cued","Uncued"),fill=farben,xjust=1,yjust=1)

# Plots: Saccade data
farben <- c("blue","yellow")
ttxt <- c("Person","Face","Body")

for (i in 1:3) {
  st <- (17:19)[i]
  
  # Fixation density
  m  <- cbind(apply(et.dfw[et.dfw$group=="free",c(st,st+3)],2,mean),
              apply(et.dfw[et.dfw$group=="mem",c(st,st+3)],2,mean))
  se <- cbind(apply(et.dfw[et.dfw$group=="free",c(st,st+3)],2,sd)/sqrt(sum(et.dfw$group=="free")),
              apply(et.dfw[et.dfw$group=="mem",c(st,st+3)],2,sd)/sqrt(sum(et.dfw$group=="mem")))
  
  yrng <- c(0,max(m+se))
  
  x <- barplot(m,beside=TRUE,col=farben,ylim=yrng,xlab="",ylab="% of total fixation time")
  arrows(x,m-se,x,m+se,length=0.03,angle=90,code=3,col="black")
  axis(1,apply(x,2,mean),c("Free viewing","Explicit encoding"),tick=FALSE)
  
  title(ttxt[i])
}

legend(max(x),max(yrng),c("Cued","Uncued"),fill=farben,xjust=1,yjust=1)
```


# # Anova by Matthias
```{r}
require("car")

# Fixations Face + Body(?) in Free Viewing vs. Explicit Encoding
ergtab <- numeric()
for (st in seq(5,16,4)) { # Variables 5:16, every 4th: fix.face and fix.body; fixn.face and ...
  msd <- c(mean(et.dfw[et.dfw$group=="free",st]),sd(et.dfw[et.dfw$group=="free",st]),
           mean(et.dfw[et.dfw$group=="mem",st]),sd(et.dfw[et.dfw$group=="mem",st]))
  teststat <- t.test(et.dfw[,st] ~ et.dfw$group)
  
  ergtab <- rbind(ergtab,c(msd,teststat$parameter,teststat$statistic,teststat$p.value))
}

colnames(ergtab) <- c("M(free)","SD(free)","M(mem)","SD(mem)","df","t","p")
rownames(ergtab) <- c("fix.face","fixn.face","fixlat.face")
print(ergtab)

# ANOVA Fixations characteristics
## 2 (Group) x 2 (Gaze) ANOVA
icond <- gl(2,1,labels=c("cued","uncued"))
idata <- data.frame(icond)

for (st in seq(7,16,4)) { # # Variables 5:16, every 4th: fix.gace and fix.nogaze; fixn.gaze and ...
  carmod <- lm(as.matrix(et.dfw[,st:(st+1)]) ~ et.dfw$group)
  print(Anova(carmod, idata=idata, idesign=~icond, type="III"))
}

# ANOVA Saccades
## 2 (Group) x 2 (Gaze) ANOVA
for (st in 17:19) {
  carmod <- lm(as.matrix(et.dfw[,c(st,st+3)]) ~ et.dfw$group)
  print(Anova(carmod, idata=idata, idesign=~icond, type="III"))
}

```

# # Memory by Matthias, nicht angepasst.
```{r}
########################################################################
# Projekt: Joint Attention & Gaze Following
# Projektarbeit Sommersemester 2017
#
# - Free Recall analysieren

#options(warn=0)

rm(list=ls())

path <- "/Users/gamer/Documents/UKE/Lehre/2017_SS/Projektarbeit/Experiment/Data/Memory/"
savepath <- "/Users/gamer/Documents/UKE/Lehre/2017_SS/Projektarbeit/Experiment/Auswertung/"

# ALL DATA
vpn <- paste("vpja",ifelse(c(1:78,81:96)<10,"0",""),c(1:78,81:96),sep="")
bed <- rep(c("free","mem"),47)

# ORIGINALLY ACQUIRED DATA
#vpn <- paste("vpja",ifelse(c(1:78)<10,"0",""),c(1:78),sep="")
#bed <- rep(c("free","mem"),39)

# Loop over subjects
erg <- numeric()
for (vp in vpn) {
  print(vp)
  
  prot <- read.csv2(paste(path,vp,".csv",sep=""))

  # Item recalled
  gaze <- sum(prot$memgazedat)
  nogaze <- sum(prot$memnongazedat)
  
  erg <- rbind(erg,c(gaze,nogaze))
}

out <- data.frame(code=vpn,bed,erg)               
names(out) <- c("code","bed","memgaze","memnogaze")
write.csv2(out,paste(savepath,"Memory.csv",sep=""),row.names=FALSE,quote=FALSE)

####################################################
# Plots
x11()

farben <- c("red","blue")

# Fixation density
m  <- cbind(apply(out[out$bed=="free",3:4],2,mean),
            apply(out[out$bed=="mem",3:4],2,mean))
se <- cbind(apply(out[out$bed=="free",3:4],2,sd)/sqrt(sum(out$bed=="free")),
            apply(out[out$bed=="mem",3:4],2,sd)/sqrt(sum(out$bed=="mem")))


x <- barplot(m,beside=TRUE,col=farben,ylim=c(0,10),xlab="",ylab="% of total fixation time")
arrows(x,m-se,x,m+se,length=0.03,angle=90,code=3,col="black")
axis(1,apply(x,2,mean),c("Free viewing","Explicit encoding"),tick=FALSE)

legend(min(x),10,c("Gazed at object","Non-gazed at object"),fill=farben,xjust=0,yjust=1)


####################################################
# ANOVAs
require("car")
require("afex")

# Recalled items
# 2 (Condition) x 2 (Gaze) ANOVA (auf erinnerte Details)
imem <- gl(2,1,labels=c("cued","uncued"))
idata <- data.frame(imem)

# Car
carmod <- lm(as.matrix(out[,3:4]) ~ out$bed)
print(Anova(carmod, idata=idata, idesign=~imem, type="III"))

```




Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).







