---
title             : "Working title: Presence of persons in naturalistic scenes - A conceptual replication"
shorttitle        : "Presence of persons in a naturalistic scene"

author:
  - name          : "Jonas Großekathöfer"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Marcusstraße 9-11, 97070 Würzburg"
    email         : "jonas.grossekathoefer@uni-wuerzburg.de"
  - name          : "Kristina Suchotzki"
    affiliation   : "1"
  - name          : "Matthias Gamer"
    affiliation   : "1"  

affiliation:
  - id            : "1"
    institution   : "Julius-Maximilian University, Würzburg"

author_note: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
library("papaja")
```

```{r analysis_preferences}
# Seed for random number generation
set.seed(42)
```

# Introduction

1) Replikationsstudie
2) Top-Down Modulationm/Anfälligket
	1. & Konsequenzen
3) Nur soziale Komponente

## Hypothesess

### H1:
Betrachtungsdauer auf das gecuete Objekt ist länger als die Betrachtungsdauer auf das ungecuete Objekt. Der Unterschied in der Betrachtungsdauer zwischen gecuetem und ungecuetem Objekt ist in der Erinnerungsbedingung geringer als in der „free-viewing“-Bedingung.
--> Fixation duration: Haupteffekt icond[*],Interaktion[ ]

### H2:
Es gehen mehr Sakkaden vom Kopf zum gecueten Objekt als zum ungecueten. Dieser Unterschied ist in der „free-viewing“-Bedingung größer als in der Erinnerungsbedingung.
--> sac fgaze: haupteffekt icond[***], Interaktion [ ]


### H3:
In der „free-viewing“-Bedingung werden gecuete Objekte besser erinnert als ungecuete Objekte.

### H4:
Je höher der Score auf der Soziale Kompetenz Skala desto höher der relative Betrachtungsdauer der gecueten Objekte im Vergleich zu den ungecueten.


# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants
In this study 96 observers (65 female and 29 male) between 18 and 55 years (M = 24.73, SD = 5.04) participated voluntarily. All observer had normal or corrected vision and were recruited at the University of Würzburgs online subject pool or by blackboard. For participation observers recieved study credit or 5€.

## Stimuli and Apparatus
The experimental stimuli consisted 26 different scenes with a single individual in the center looking at one of two objects of interests in the right or left half of the photography. The direction of the gaze cue and the place of the objects were balanced, creating 104 unique naturalistic scenes in the end. For each participant, a set was randomly generated from this pool containing each scene only once, resulting in 26 trials with exclusive scenes. Eye movements were recorded with an EyeLink1000
tower system, sampling at 1000 Hz.

## Design & Procedure
A two-level (instruktcion: free viewing/ explicit encoding) between subjects factor and a two-level (reference: cued/uncued) within subjects factor was manipulated in the experiment. After giving full informed consent, the eye-tracker was callibrated for each observer. Observers were then told either that there is a foolow-up memory test or nothing. The presentation of the stimuli was randomized. In each trial the scene was present for 10 seconds. Observers were told to look at the scene as they would look at photographs. Intertrial intervall was randomized between 2 and 4 seconds. After the last trial participants filled in questionnaires (demographics, autism-questionnaire (short), and Inventar soziale kompetenz) and were asked to recall as many items as possible in a free recall memory-test. Afterwards participants recieved their credit.


## Data analysis
Regions-of-Interest were hand-drawn around the relevant objects and the individual in the center. Aditionally the ROI were color-coded for cued and uncued objects and also for the head and body of the individual on the photography to determine gaze locations. Outlier detection.

We used `r cite_r("r-references.bib")` for all our analyses.


# Results

## Viewing behavior

Priorization of the gazed-at object was measuerd in mulitple ways.

### Fixation duration (H1)
To investigate the first hypothisis the relative cumulative fixation duration is calculated as time duration on an Ooi divided by the time spent on the scene during presentation. It shows a bias towards the gazed-at object, which was fixated longer. This was suported by the corresponding ANOVA wich revealed a significant main effect for reference, `r apa.fix.gaze$full_result$icond, for condition` `r apa.fix.gaze$full_result$et_dfw_group which was unaffected by the two-way interaction condition` `r apa.fix.gaze$full_result$et_dfw_group_icond`.

### Leaving saccades (H2)
The second hypothisis predicts, that there are more saccades leaving from the head to the gazed-at object compared to the uncued. Furthermore it is claimed, that an interaction is increasing the difference between the conditions. An Anova supports the first claim, there is an significant main effect for reference, `r apa.sac.fgaze$full_result$icond`, but no confirmation was found for the predicted interaction between reference and instruction `r apa.sac.fgaze$full_result$et_dfw_group_icond`.


### Fixation latency
Fixation latency, for each OOI  the mean out of all first fixations on after stimulus onset, showed, that gazed-at OOI, `r apa.fixlat.gaze$full_result$icond` are looked at earlier. The same is true for OOI in the memory-condition, `r apa.fixlat.gaze$full_result$et_dfw_group`, but with out interaction, `r apa.fix.gaze$full_result$et_dfw_group_icond`.

### Memory
Observer remind OOI equally well, regardless of reference `r apa.mem$full_result$df_w_mem_bed`or instrucition `r apa.mem$full_result$imem`.


#### Objects

### Fixation number
The number of fixations of a ROI during scene presentation was counted and divided by the total number of fixations during scene presentation, to calculate a measure of fixation proportion.

#### Objects





### Leaving saccades

#### Head (vs. Body (t-test))
Fixation patterns for the individual between the two groups differ only for faces. Overall, there is no difference in the viewing pattern for the bodys (all T < .25). For the faces especially the latency of first fixations differs (t,p). In the free recoding condition fixations are 242 ms earlier compared to the explicit encoding condition. Fixation duration and number of fixation does not differ between conditions.  

## Memory task

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
