---
title             : "Working title: Presence of persons in naturalistic scenes - A conceptual replication"
shorttitle        : "Presence of persons in a naturalistic scene"

author:
  - name          : "Jonas Großekathöfer"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Marcusstraße 9-11, 97070 Würzburg"
    email         : "jonas.grossekathoefer@uni-wuerzburg.de"
  - name          : "Kristina Suchotzki"
    affiliation   : "1"
  - name          : "Matthias Gamer"
    affiliation   : "1"  

affiliation:
  - id            : "1"
    institution   : "Julius-Maximilian University, Würzburg"

author_note: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.

keywords          : "keywords"
wordcount         : "X"

bibliography      : 
  - "r-references.bib"
  - "repl-zwickel-2017.bib"

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}

library("papaja")
library("tidyverse")
library("car")
library("afex")
library("ggpubr")

```

```{r paths}

rm(list=ls())

pathMEM <- "data/Memory/"
pathET <- "data/prot/"
pathFB <- "data/FB/"

```

```{r Reading eye tracking data in, warning = FALSE, message = FALSE}

# ALL EYE TRACKING DATA
vpn <- paste0("vpja",ifelse(c(1:78,81:96)<10,"0",""),c(1:78,81:96))
bed <- rep(c("free","mem"),47)

# ORIGINALLY ACQUIRED DATA
#vpn <- paste0("vpja",ifelse(c(1:78)<10,"0",""),c(1:78))
#bed <- rep(c("free","mem"),39)

bed <- bed[!(vpn %in% "vpja23")]  # missing data
vpn <- vpn[!(vpn %in% "vpja23")]  

# Loop over subjects
erg <- numeric(); nvalid <- numeric(); cleantime <- numeric()
for (vp in vpn) {
  #  print(vp)

  prot <- read.csv2(paste0(pathET,vp,"_Fixations.csv"))

  # Restrict to trials with valid baseline?
  nvalid <- c(nvalid,sum(prot$blok==1))
  prot <- prot[prot$blok==1,]

  cleantime <- c(cleantime,mean(prot$cleantime))

  erg <- rbind(erg,apply(prot[,8:ncol(prot)],2,mean,na.rm=TRUE))
}

df.w.et <- data.frame(code=vpn,group=bed,nvalid,cleantime,erg)


df.l.et <- gather(df.w.et, key, value, fix.face:sac.bnongaze, factor_key=TRUE) %>%
  mutate(
    key = as.character(key),
    fixations =
      as.factor(
        ifelse(startsWith(key, "fix."), "fix",
             ifelse(startsWith(key, "fixn."), "fixn",
                    ifelse(startsWith(key, "fixlat."), "fixlat",
                           ifelse(startsWith(key, "sac."), "sac", NA))))),
    region =
      as.factor(
        ifelse(endsWith(key, ".face"), "face",
               ifelse(endsWith(key, ".body"), "body",
                      ifelse(endsWith(key, ".gaze"), "gaze",
                             ifelse(endsWith(key, ".nongaze"), "nongaze",
                                    ifelse(endsWith(key, ".pgaze"), "pgaze",
                                           ifelse(endsWith(key, ".fgaze"), "fgaze",
                                                  ifelse(endsWith(key, ".bgaze"), "bgaze",
                                                         ifelse(endsWith(key, ".pnongaze"), "pnongaze",
                                                                ifelse(endsWith(key, ".fnongaze"), "fnongaze",
                                                                       ifelse(endsWith(key, ".bnongaze"), "bnongaze",NA)))))))))))) %>%
  arrange(code)

rm(prot, bed, cleantime, nvalid, vp, vpn, erg)

```

```{r Reading memory data in, warning = FALSE, message = FALSE}

# ALL MEMORY DATA
vpn <- paste0("vpja",ifelse(c(1:78,81:96)<10,"0",""),c(1:78,81:96))
bed <- rep(c("free","mem"),47)

# ORIGINALLY ACQUIRED DATA
#vpn <- pasteo("vpja",ifelse(c(1:78)<10,"0",""),c(1:78))
#bed <- rep(c("free","mem"),39)

# Loop over subjects
erg <- numeric()
for (vp in vpn) {
  # print(vp)

  prot <- read.csv2(paste0(pathMEM,vp,".csv"))

  # Item recalled
  gaze <- sum(prot$memgazedat)
  nogaze <- sum(prot$memnongazedat)

  erg <- rbind(erg,c(gaze,nogaze))
}

df.w.mem <- data.frame(code=vpn,bed,erg)               
names(df.w.mem) <- c("code","bed","memgaze","memnogaze")

rm(gaze, nogaze, erg, prot, bed, vp, vpn)

```

```{r Reading questionnaire data in, warning = FALSE, message = FALSE}

df.w.demo <- read_csv2(paste0(pathFB,"Projektarbeit_Dateneingabemaske.csv")) %>%
  transmute(
    vp = as.factor(VP_Nr),
    sex = as.factor(Demo_Sex),
    age = Demo_Alter,
    aq_social = ifelse((5-AQK_1) < 3, 1, 0) + ifelse((5-AQK_7) < 3, 1, 0) + ifelse(AQK_8 < 3, 1, 0) + ifelse((5-AQK_10) < 3, 1, 0) + ifelse((5-AQK_11) < 3, 1, 0) + ifelse(AQK_13 < 3, 1, 0) + ifelse((5-AQK_14) < 3, 1, 0) + ifelse((5-AQK_20) < 3, 1, 0) + ifelse((5-AQK_24) < 3, 1, 0) + ifelse((5-AQK_28) < 3, 1, 0) + ifelse((5-AQK_31) < 3, 1, 0), # 5- 'item' for reversed items, then if 1/2 -> 1, 3/4 -> 0  
    aq_imagination = ifelse((5-AQK_3) < 3, 1, 0) + ifelse((5-AQK_5) < 3, 1, 0) + ifelse((5-AQK_6) < 3, 1, 0) + ifelse((5-AQK_9) < 3, 1, 0) + ifelse((5-AQK_16) < 3, 1, 0) + ifelse((5-AQK_17) < 3, 1, 0) + ifelse((5-AQK_18) < 3, 1, 0) + ifelse((5-AQK_22) < 3, 1, 0) + ifelse((5-AQK_23) < 3, 1, 0) + ifelse((5-AQK_26) < 3, 1, 0) + ifelse((5-AQK_32) < 3, 1, 0) + ifelse((5-AQK_33) < 3, 1, 0),
    aq_communication = ifelse(AQK_2 < 3, 1, 0) + ifelse(AQK_4 < 3, 1, 0) + ifelse(AQK_12 < 3, 1, 0) + ifelse(AQK_15 < 3, 1, 0) + ifelse(AQK_19 < 3, 1, 0) + ifelse(AQK_21 < 3, 1, 0) + ifelse(AQK_25 < 3, 1, 0) + ifelse(AQK_27 < 3, 1, 0) + ifelse(AQK_29 < 3, 1, 0) + ifelse(AQK_30 < 3, 1, 0),
    aq_sumscore = ifelse((5-AQK_1) < 3, 1, 0) + ifelse(AQK_2 < 3, 1, 0) + ifelse((5-AQK_3) < 3, 1, 0) + ifelse(AQK_4 < 3, 1, 0) + ifelse((5-AQK_5) < 3, 1, 0) + ifelse((5-AQK_6) < 3, 1, 0) + ifelse((5-AQK_7) < 3, 1, 0) + ifelse(AQK_8 < 3, 1, 0) + ifelse((5-AQK_9) < 3, 1, 0) + ifelse((5-AQK_10) < 3, 1, 0) + ifelse((5-AQK_11) < 3, 1, 0) + ifelse(AQK_12 < 3, 1, 0) + ifelse(AQK_13 < 3, 1, 0) + ifelse((5-AQK_14) < 3, 1, 0) + ifelse(AQK_15 < 3, 1, 0) + ifelse((5-AQK_16) < 3, 1, 0) + ifelse((5-AQK_17) < 3, 1, 0) + ifelse((5-AQK_18) < 3, 1, 0) + ifelse(AQK_19 < 3, 1, 0) + ifelse((5-AQK_20) < 3, 1, 0) + ifelse(AQK_21 < 3, 1, 0) + ifelse((5-AQK_22) < 3, 1, 0) + ifelse((5-AQK_23) < 3, 1, 0) + ifelse((5-AQK_24) < 3, 1, 0) + ifelse(AQK_25 < 3, 1, 0) + ifelse((5-AQK_26) < 3, 1, 0) + ifelse(AQK_27 < 3, 1, 0) + ifelse((5-AQK_28) < 3, 1, 0) + ifelse(AQK_29 < 3, 1, 0) + ifelse(AQK_30 < 3, 1, 0) + ifelse((5-AQK_31) < 3, 1, 0) + ifelse((5-AQK_32) < 3, 1, 0) + ifelse((5-AQK_33) < 3, 1, 0))

```

# Introduction

Humans relie on the information other humans provide. This does not only holds for the explicit conversations but also to implicit alginment of attention to objects. These alingment of attention can sometimes be observed by otheres by processing the direction of the body, head and most importantly the eyes. For the eyes this momentum is called gaze following.

Multiple studies show, that observed congruent gaze cues resluts in an processing benefit for that location. So showed @Driver1999 and @Friesen1998 that... they have in come that they were all highly controlled laboratory studies

## social attention
An superior and more applicabale framework of this research proviedes the research to social attention [for a review see @Frischen2007a]. To social attention is reffered, when observer are confronted with social stimuli, multiple studies show a strong advantage for these stimuli. The process wehre human aling their visual attention to an object or place fixated by another indivuduum is called joint attention. joint attention was, like a lot of gaze cuing research showen often in an controlled labororatory setting to work.
## zwickel description
@Zwickel2010 showed that these effects are also valid for more naturalistic scenes. In an free-viewing paradigm they presented their subjects computer rendered scenes for multiple seconds. The scences contained a referencing object, either a human or an oriented loudspeaker, and two objects from which one was referenced. They showed that even without an specific task subjects spontaneously priorize the attentional focus of the shown subject, but did not reacted to the orientation of the loudspeaker. In line with predicitions by the social attention, the most priorized region was stil the head of the shown individual, but the referenced obejct was fixated remarkably earlier compared with the not referenced object. Underlining the social component of this effect, this was only valid for the person in the scene and did not hold for loudspeaker. Unfortunaltly @Zwickel2010 only had a small sample (n=16) and therefore only little power. As power becomes more important these days, in this study we tried to replicate their finding and overcome this short coming. 

## comparison to our study
However, this is an conceptual replication. It is aimed at replicating the main findings of @Zwickel2010, and extend in other aspects. One concern from the @Zwickel2010 study comes from, the used computer generated stimuli. To be even closer  as @Zwickel2010 to a naturalistic stimuli, photographies are chosen over computer rendered scene. As often, by being more naturalistic experimental control is reduced. The consequences are hold to an minimum by producing stimuli the same way (each scene 4 times, with the individual looking twice to the left and right top each object). But still, in real photographs small changes are unavoidable. Whereas @Zwickel2010 only rotate the figure in the scene, another photography was taken. As consequence, for example the body orientation is not perfectly controlled anymore and might differ slightly between photographies.
Aditionally it is also investigated whether top-down modulations affects these joint and social attention effects in naturalistic scenes. So half of subjects are told that there is an memory task afterwards. The other half of subjects is compareable to @Zwickel2010 social-conditon. The condition with the loudspeaker is not replicated. So in this study the focuses only on the social component of @Zwickel2010, and extends it by top-down modulation. 



Motivation:
1) Replikationsstudie
 mit mehr power!
2) Top-Down Modulation/Anfälligket
	1. & Konsequenzen
3) Nur soziale Komponente


## Hypothesis

### joint attention/gaze following
The first attempt of this study is to replicate [@Zwickel2010] findings.

#### H1
Consequently, as in @Zwickel2010, a priorisation for the gazed-at OOI is predicted. This  priorisation can be measuered in multiple ways. First there should be an early fixation bias towards the gazed-at object. During presentation time, the total time that the gazed-at object is fixated should be prolonged, with more fixations as well. For saccades it is expected, that saccades leaving from the head are more likely to move to the gazed-at object, in contrast to the not-gazed-at object. (Maineffect icond, Anova)

#### H2
New, compared to @Zwickel2010's study, is the instruction condtion. For gaze-following it is expected that the exclusive priorisation for the gazed-at object will decrease for subjects in explicit-encoding group, due to the explicit processing of the scene. This means smaller differences in the fixation measurements are expected. For leaving saccades it is also expected that the under H1n stated effect decreases. (1st: Interaction group:icond)
(?!Hypothese zu Gruppen, dass expplicit mehr focus auf Gegensätnde richtet, da anweisung? (Maineffect group)

#### H3
Also new is the follow-up memory test for the OOI. First it is assumed, that subjects with announced memory test will recall more items, because they process the scenes more thorough. Aditionally it is expected, that in the free-recall condition gazed-at objects are better recalled then not-gazed at objects. 

### social attention

#### H4
As naturalistic scences are used, the basic effects of social attention are expected. This means, that the head will be priorized over the body. This priorisation can be measuered, in multiple ways. And again, it is expected, that first fixation fell earlier on the head, that it is fixated longer and more often then the body. Additionally it is also expected, that the fixations occure earlier, then on the gazed-at object, because the gaze-cue needs to be processed in advance. Aditionally, the head should also be fixated earlier and more often then the body.

#### H5
Due to the instruction of the memory test, and the assumed change in processing the picture, the viewing behavior should change for social stimuli. Due to explicit encoding, it is expected that the head looses some of its importance. As a consequence, the head should be prioritized stronger in the free-viewing group compared to the explicit-encoding group. Therefor it should be fixated longer, faster and more often. 


# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants
In this study 96 observers (65 female and 29 male) between 18 and 55 years (M = 24.73, SD = 5.04) participated voluntarily. All observer had normal or corrected vision and were recruited at the University of Würzburgs online subject pool or by blackboard. For participation observers recieved study credit or 5€.

## Stimuli and Apparatus
The experimental stimuli consisted 26 different scenes with a single individual in the center looking at one of two objects of interests in the right or left half of the photography. The direction of the gaze cue and the place of the objects were balanced, creating 104 unique naturalistic scenes in the end. For each participant, a set was randomly generated from this pool containing each scene only once, resulting in 26 trials with exclusive scenes. Eye movements were recorded with an EyeLink1000
tower system, sampling at 1000 Hz.

## Design & Procedure
A two-level (instruction: free viewing/ explicit encoding) between subjects factor and a two-level (reference: cued/uncued) within subjects factor was manipulated in the experiment. After giving full informed consent, the eye-tracker was callibrated for each observer. Observers were then told either that there is a foolow-up memory test or nothing. The presentation of the stimuli was randomized. In each trial the scene was present for 10 seconds. Observers were told to look at the scene as they would look at photographs. Intertrial intervall was randomized between 2 and 4 seconds. After the last trial participants filled in questionnaires (demographics, autism-questionnaire (short), and Inventar soziale kompetenz) and were asked to recall as many items as possible in a free recall memory-test. Afterwards participants recieved their credit.


## Data analysis
Regions-of-Interest were hand-drawn around the relevant objects and the face and body of the individual in the center. These ROIs were color-coded for cued and uncued objects and also for the head and body of the individual on the photography to determine gaze locations. Outlier detection.

We used `r cite_r("r-references.bib")` for all our analyses.


# Results
Priorizations of the ROIs in the scene were measuerd in mulitple ways. One observer was excluded due to missing data.

## Joint attention/ gaze following

As a measuere of priorisation fixation duration, fixation number, fixation latency, as well as leaving saccades are used.

### Fixations
```{r TO-DO: Plots fixations joint, warining = FALSE, message = FALSE}

```

```{r Descriptives fixations joint, warining = FALSE, message = FALSE}

# Descriptives for fixation chacracteristics for joint attention

dscr.fixjoi <- df.w.et %>% summarise(mean(fix.gaze), sd(fix.gaze), mean(fix.nongaze), sd(fix.nongaze), mean(fixn.gaze), sd(fixn.gaze), mean(fixn.nongaze), sd(fixn.nongaze), mean(fixlat.gaze), mean(fixlat.nongaze), sd(fixlat.nongaze))
dscr.fixjoi.group <- df.w.et %>% group_by(group) %>% summarise(mean(fix.gaze), sd(fix.gaze), mean(fix.nongaze), sd(fix.nongaze), mean(fixn.gaze), sd(fixn.gaze), mean(fixn.nongaze), sd(fixn.nongaze), mean(fixlat.gaze), sd(fixlat.gaze), mean(fixlat.nongaze), sd(fixlat.nongaze))

```

```{r Anova fixations joint, warning = FALSE, message = FALSE}

# ANOVA Fixations characteristics for joint attention
## 2 (Group) x 2 (Gaze) ANOVA

icond <- gl(2,1,labels=c("cued","uncued")) # within-factor
idata <- data.frame(icond)

for (st in seq(7,16,4)) { # Variables 7:16, every 4th: fix.gaze and fix.nogaze; fixn.gaze and ...
  carmod <- lm(as.matrix(df.w.et[,st:(st+1)]) ~ df.w.et$group)
  #print(Anova(carmod, idata=idata, idesign=~icond, type="III"))
  assign(paste0("anova.",colnames(df.w.et)[st]), Anova(carmod, idata=idata, idesign=~icond, type="III"))
  assign(paste0("apa.anova.",colnames(df.w.et)[st]), apa_print(Anova(carmod, idata=idata, idesign=~icond, type="III"), correction="GG", mse = FALSE))
  }

rm(carmod, idata, icond, st)

```

#### Fixation duration (H1, H2)
The relative cumulative fixation duration is calculated as time duration on an OOI divided by the time spent fixating the rest of the scene. It shows a bias towards the gazed-at object, which was fixated significantly longer (see Table/Figure) and confirms [@Zwickel2010]'s findings. As predicted the corresponding ANOVA revealed a significant main effect for reference, `r apa.anova.fix.gaze$full_result$icond` and for condition `r apa.anova.fix.gaze$full_result$df_w_et_group`. Against prediction their was no effect of the two-way interaction, `r apa.anova.fix.gaze$full_result$df_w_et_group_icond`.


#### Fixation latency (H1, H2)
An additional measurement of priorisation is fixation latency, that is for each OOI  the mean out of all first fixations after stimulus onset. In line with [@Zwickel2010], an object is fixated earlier when it is gazed-at. But also when the observer was in the explicit encoding condition. The statistical significance is confirmed by an ANOVA: for reference `r apa.anova.fixlat.gaze$full_result$icond` and condition, `r apa.anova.fixlat.gaze$full_result$df_w_et_group`). For fixation latency with a trend(?) for an interaction, `r apa.anova.fixlat.gaze$full_result$df_w_et_group_icond`.

#### Fixation number (H1, H2)
As a third measurement of priorisation, fixation number, as the count of fixations per ROI during scene presentation, divided by the total number of fixations during scene presentation, was calculated. It shows, that OOI were fixated more often when gazed-at `r apa.anova.fixn.gaze$full_result$icond`, again in line with [@Zwickel2010]. Objects were also more often fixated in the explicit encoding condition`r apa.anova.fixn.gaze$full_result$df_w_mem`, and again against prediction there was no interaction, `r apa.anova.fixn.gaze$full_result$df_w_et_group_icond`.
 

### Saccades
```{r Anova saccades, warning=FALSE, message=FALSE}
# ANOVA Saccades
## 2 (Group) x 2 (Gaze) ANOVA

icond <- gl(2,1,labels=c("cued","uncued")) # within-factor
idata <- data.frame(icond)

for (st in 17:19) {
  carmod <- lm(as.matrix(df.w.et[,st:(st+1)]) ~ df.w.et$group)
  #print(Anova(carmod, idata=idata, idesign=~icond, type="III"))
  assign(paste0("anova.",colnames(df.w.et)[st]), Anova(carmod, idata=idata, idesign=~icond, type="III"))
  assign(paste0("apa.anova.",colnames(df.w.et)[st]), apa_print(Anova(carmod, idata=idata, idesign=~icond, type="III"), correction="GG", mse = FALSE))
  }

dscr.sac <- df.w.et %>% summarise(mean(sac.pgaze), sd(sac.pgaze), mean(sac.pnongaze), sd(sac.pnongaze), mean(sac.fgaze), sd(sac.fgaze), mean(sac.fnongaze), sd(sac.fnongaze), mean(sac.bgaze), sd(sac.bgaze), mean(sac.bnongaze), sd(sac.bnongaze))
dscr.sac.group <- df.w.et %>% group_by(group) %>% summarise(mean(sac.pgaze), sd(sac.pgaze), mean(sac.pnongaze), sd(sac.pnongaze), mean(sac.fgaze), sd(sac.fgaze), mean(sac.fnongaze), sd(sac.fnongaze), mean(sac.bgaze), sd(sac.bgaze), mean(sac.bnongaze), sd(sac.bnongaze))

rm(carmod, idata, icond, st)
```

#### Leaving saccades (H1, H2)
The second hypothesis predicts, that there are more saccades leaving from the head to the gazed-at object. Furthermore it is claimed, that an interaction between instruction and reference results in increasing differences in the free-viwing condition. An Anova supports the first claim. There is an significant main effect for reference, `r apa.anova.sac.fgaze$full_result$icond`, but no confirmation was found for the predicted interaction between reference and instruction `r apa.anova.sac.fgaze$full_result$df_w_et_group_icond`.

### Memory (H3)
```{r Anova memory, warning=FALSE, message=FALSE}
# Recalled items
# 2 (Condition) x 2 (Gaze) ANOVA (auf erinnerte Details)

imem <- gl(2,1,labels=c("cued","uncued"))
idata <- data.frame(imem)

# Car
carmod <- lm(as.matrix(df.w.mem[,3:4]) ~ df.w.mem$bed)
#print(Anova(carmod, idata=idata, idesign=~imem, type="III"))
anova.mem <- Anova(carmod, idata=idata, idesign=~imem, type="III")
apa.anova.mem <- apa_print(Anova(carmod, idata=idata, idesign=~imem, type="III"), correction="GG", mse = FALSE)

dscr.mem <- df.w.mem %>% summarise(mean(memgaze), sd(memgaze), mean(memnogaze), sd(memnogaze))
dscr.mem.group <- df.w.mem %>% group_by(bed) %>% summarise(mean(memgaze), sd(memgaze), mean(memnogaze), sd(memnogaze))

rm(imem, idata, carmod)
```
The free-recall test showed, that unsurprisingly observers with explicit encoding remembered on average 2 items more then observers from the other group. An Anova proved this effect as statistically significant, `r apa.anova.mem$full_result$df_w_mem_bed`. Referencing an OOI did not influence memory performance, `r apa.anova.mem$full_result$imem`. There was also no interaction, `r apa.anova.mem$full_result$df_w_mem_bed_imem`.


## Social attention
A similar pattern to the OOI can be seen when comparing the head with the body region. Again there were the same measurements to acount for priorisation. 

```{r TO-DO: Plots fixations social, warining = FALSE, message = FALSE}

```

```{r Descriptives fixations social, warining = FALSE, message = FALSE}

# Descriptives for fixation chacracteristics for social attention

dscr.fixsoc <- df.w.et %>% summarise(mean(fix.face), sd(fix.face), mean(fix.body), sd(fix.body), mean(fixn.face), sd(fixn.face), mean(fixn.body), sd(fixn.body), mean(fixlat.face), sd(fixlat.face), mean(fixlat.body), sd(fixlat.body))
dscr.fixsoc.group <- df.w.et %>% group_by(group) %>% summarise(mean(fix.face), sd(fix.face), mean(fix.body), sd(fix.body), mean(fixn.face), sd(fixn.face), mean(fixn.body), sd(fixn.body), mean(fixlat.face), sd(fixlat.face), mean(fixlat.body), sd(fixlat.body))
```

```{r Anova fixations social, warning = FALSE, message = FALSE}
# ANOVA Fixations characteristics
## 2 (Group) x 2 (Face/Body) ANOVA

icond <- gl(2,1,labels=c("head","body")) # within-factor
idata <- data.frame(icond)

for (st in seq(5,16,4)) { # Variables 5:16, every 4th: fix.face and fix.noface; fixn.face and ...
    carmod <- lm(as.matrix(df.w.et[,st:(st+1)]) ~ df.w.et$group)
  #print(Anova(carmod, idata=idata, idesign=~icond, type="III"))
  assign(paste0("anova.",colnames(df.w.et)[st]), Anova(carmod, idata=idata, idesign=~icond, type="III"))
  assign(paste0("apa.anova.",colnames(df.w.et)[st]), apa_print(Anova(carmod, idata=idata, idesign=~icond, type="III"), correction="GG", mse = FALSE))
  }


rm(carmod, idata, icond, st)

```
Analysis for the social attention part contained again Anovas for the different dependent variabels indicating priorisation.

### Face vs body fixation (H4)
The first measurement shows, that faces were fixated longer then the body  (Table X), `r apa.anova.fix.face$full_result$icond`, but there is no difference between the instruction-groups, `r apa.anova.fix.face$full_result$df_w_et_group`, and no interaction (trend) between the two factors, `r apa.anova.fix.face$full_result$df_w_et_group_icond`.
The same pattern can be seen for fixation number, where there is a strong effect for region, with more fixations on the face, `r apa.anova.fixn.face$full_result$icond` and no difference between the instructions, `r apa.anova.fixn.face$full_result$df_w_et_group`, and no interaction `r apa.anova.fixn.face$full_result$df_w_et_group_icond`.
Latencies of fixation differed also remarkly between head and body, but only for region `r apa.anova.fixlat.face$full_result$icond`. There was neither an effect for interstruction, `r apa.anova.fixlat.face$full_result$df_w_et_group` nor was their an interaction, `r apa.anova.fixlat.face$full_result$df_w_et_group_icond`.

### Free-viewing vs explicit-encoding face fixations (H5)
```{r Plots free vs mem face fixations, warning = FALSE, message = FALSE}

# plots

plot.face.free_vs_mem <- df.l.et %>%
  filter(fixations=="fix" & region=="face") %>%
  ggboxplot(x = "fixations", y = "value",
                color = "group", palette =c("#00AFBB", "#E7B800", "#FC4E07"),
                add = "jitter", shape = "group") +
  stat_compare_means()
plot.face.free_vs_mem

```

```{r T-test face fixations, warning = FALSE, message = FALSE}

# Fixations Face in Free Viewing vs. Explicit Encoding

for (st in seq(5,16,4)) {
  msd <- c(mean(df.w.et[df.w.et$group=="free",st]),sd(df.w.et[df.w.et$group=="free",st]),
           mean(df.w.et[df.w.et$group=="mem",st]),sd(df.w.et[df.w.et$group=="mem",st]))
  teststat <- t.test(df.w.et[,st] ~ df.w.et$group)
  
  assign(paste0("ttest.",colnames(df.w.et)[st]), data.frame(M.free=msd[1],SD.free=msd[2], M.mem=msd[3], SD.mem=msd[4],  df=teststat$parameter, t=teststat$statistic, p=teststat$p.value))
 
  assign(paste0("apa.ttest.",colnames(df.w.et)[st]), apa_print(t.test(df.w.et[,st] ~ df.w.et$group)))
  }


rm(msd, teststat, st) 

```

A t-test between face fixation for the different groups provides information whether faces are differently processed dependent on the insturction observers get. Only fixation latency differed significantly between groups, `r apa.ttest.fixlat.face$full_result`, with faster fixations for the free viewing group. For fixation duration there was only a trend for difference between groups, `r apa.ttest.fix.face$full_result`. And fixation number did not differ, `r apa.ttest.fixn.face$full_result`.   

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
