---
title: "Supplementary Material"
output: bookdown::word_document2

---

<!--

To reproduce the exact word file, change by hand:
  add cover page and remove title
  p and f in tables to italics
  ges into $\hat{\eta}^2_G$
  move tables to new page
  
-->

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo=FALSE, warning = FALSE)

source("../02_scripts/01-libraries.R")
source("../02_scripts/02-paths.R")
theme_set(theme_cowplot())

```

```{r load packages and data}

source(path(path_scripts_data, "eyetracking.R"))
source(path(path_scripts_data, "memory.R"))
source(path(path_scripts_data, "questionnaire.R"))
source(path(path_scripts_data, "rois.R"))

```

## S1 Regions of Interest (ROIs) ##

```{r}

source(path(path_scripts_analysis, "dscr_roi.R"))

```

### List of all ROIs ###

In our study, each scene contained two central objects. Below is the full list
of all objects presented in the scenes. Note that objects were counterbalanced
regarding cueing (i.e., being cued or uncued) and image side (i.e., appearing on
the left or right side of the scene).

|     stim_id | 1                         | 2                |
| :---------: | :-----------------------: | :--------------: |
|          01 | orange                    | melon            |
|          02 | punches                   | roller stick     |
|          03 | bike helmet               | stethoscope      |
|          04 | rack                      | ventilator       |
|          05 | *blackroll*               | hair dryer       |
|          06 | fruit bowl                | globe            |
|          07 | toaster                   | thermos flask    |
|          08 | marmalade                 | watch            |
|          09 | cup                       | water bottle     |
|          10 | brush                     | glasses          |
|          11 | chair                     | bucket           |
|          12 | binoculars                | camera           |
|          13 | book                      | laptop           |
|          14 | headphones                | folder           |
|          15 | water glass               | towel            |
|          16 | baggage                   | cap              |
|          17 | strawberries              | shoe             |
|          18 | ukulele                   | hand brush       |
|          19 | drum                      | hat              |
|          20 | bowl                      | cushions         |
|          21 | pencil                    | smartphone       |
|          22 | feather                   | elephant         |
|          23 | saw                       | hammer           |
|          24 | flower                    | jug              |
|          25 | coffee grinder            | candle           |
|          26 | bulb                      | flashlight       |

### ROI size, position and distance ###

Each scene contained five regions: Background, Head, Body, Cued object, Uncued
object. In the following tables, a complete overview is given regarding average
ROI size in pixels, centimeters and degrees of visual angle, as well as ROI
position and distances between ROIs on image.

```{r tblSize, results='asis'}

apa_table(
    dscr_roi %>% select(roi_id, ends_with("size")),
    caption = "Sizes of the regions of interest in pixels.",
    note = "Mean [m] and standard deviation [sd]."
    , align = c("l", rep("r", 2))
    , placement = "hp")

```

&NewLine;
&NewLine;

```{r tblPx, results='asis'}

apa_table(
    dscr_roi %>% select(roi_id, ends_with("px"))
    , caption = "Width and height of regions of interest in pixels."
    , note = "Mean [m] and standard deviation [sd] of the width [w] and height [h]."
    , align = c("l", rep("r", 4))
    , placement = "hp")

```

&NewLine;
&NewLine;

```{r tblCm, results='asis'}

apa_table(
    dscr_roi %>% select(roi_id, ends_with("cm"))
    , caption = "Width and height of regions of interest in centimeters on the computer screen."
    , note = "Mean [m] and its standard deviation [sd] of the width [w] and height [h]."
    , align = c("l", rep("r", 4))
    , placement = "hp")

```

&NewLine;
&NewLine;

```{r tblDg, results='asis'}

apa_table(
    dscr_roi %>% select(roi_id, ends_with("dg"))
    , caption = "Width and height of regions of interest in degrees of visual angle for the current viewing distance. "
    , note = "Mean [m] and its standard deviation [sd] of the width [w] and height [h]"
    , align = c("l", rep("r", 4))
    , placement = "hp")

```

&NewLine;
&NewLine;

```{r tblXy, results='asis'}

apa_table(
    dscr_roi %>%
      select(roi_id, ends_with("_x"), ends_with("_y")) %>%
      filter(roi_id != "background")
    , caption = "Positions (x- and y-coordinates) of the different regions of interest on the image in pixels relative to the top left corner."
    , note = "Mean [m] and standard deviation [sd]."
    , align = c("l", rep("r", 2))
    , placement = "hp")

```
&NewLine;
&NewLine;

Distances between the head, the cued and the uncued objects.

```{r tblDist, results='asis'}

apa_table(
    dscr_roi_dist
    , caption = "Distance between objects (cued & uncued) and the head of the depicted person in pixels, centimeters and degree of visual angle."
    , note = "Mean [m] and standard deviation [sd]."
    , align = c("l", rep("r", 6))
    , placement = "hp")

```

<P style="page-break-before: always">
## S2 Follow-up ANOVAs on social attention ##

In our main analysis the three-way interaction of Group x ROI x Time was
significant. As follow-up test separate ANOVAs for each time point were
performed to reveal time specific patterns. Only the first ANOVA is reported in
the manuscript with all relevant details due to the observed statistically
significant effects including Group and ROI. Below are all ANOVA tables for each
time point.

```{r, include=FALSE}

source(path(path_scripts_analysis, "aov_sa.R"))

```


### time point 1: 0 - 2 seconds ###

```{r tblAov1, results='asis'}

apa_table(
    aov_sa_dur_1$anova_table %>%
      rownames_to_column(var = "effect") %>%
      rename('p' = `Pr(>F)`) %>% 
      mutate(` ` = case_when(p<0.001 ~ "***",
                             p<0.01  ~ "**",
                             p<0.05 ~ "*",
                             p<0.1 ~ ".",
                             p>=.01 ~ " "),
               effect = case_when(effect == "group_id" ~ "Group",
                                  effect == "fix_id" ~ "ROI",
                                  effect == "group_id:fix_id"~ "Group x ROI")) 
    , caption = "time point 1: 0 - 2 seconds"
    , note = "MSE: mean squared error; ges: generalized eta square; * : p < .05; ** : p < .01; *** : p < .001"
    , align = c("l", rep("r", 6), "l")
    , placement = "hp")

```


### time point 2: 2 - 4 seconds ###

```{r tblAov2, results='asis'}

apa_table(
    aov_sa_dur_2$anova_table %>%
        rownames_to_column(var = "effect") %>%
      rename('p' = `Pr(>F)`) %>% 
      mutate(` ` = case_when(p<0.001 ~ "***",
                             p<0.01  ~ "**",
                             p<0.05 ~ "*",
                             p<0.1 ~ ".",
                             p>=.01 ~ " "),
               effect = case_when(effect == "group_id" ~ "Group",
                                  effect == "fix_id" ~ "ROI",
                                  effect == "group_id:fix_id"~ "Group x ROI")) 
    , caption = "time point 2: 2 - 4 seconds"
    , note = "MSE: mean squared error; ges: generalized eta square; * : p < .05; ** : p < .01; *** : p < .001"
    , align = c("l", rep("r", 6), "l")
    , placement = "hp")

```


### time point 3: 4 - 6 seconds ###

```{r tblAov3, results='asis'}

apa_table(
    aov_sa_dur_3$anova_table %>%
rownames_to_column(var = "effect") %>%
      rename('p' = `Pr(>F)`) %>% 
      mutate(` ` = case_when(p<0.001 ~ "***",
                             p<0.01  ~ "**",
                             p<0.05 ~ "*",
                             p<0.1 ~ ".",
                             p>=.01 ~ " "),
               effect = case_when(effect == "group_id" ~ "Group",
                                  effect == "fix_id" ~ "ROI",
                                  effect == "group_id:fix_id"~ "Group x ROI"))     , caption = "time point 3: 4 - 6 seconds"
    , note = "MSE: mean squared error; ges: generalized eta square; * : p < .05; ** : p < .01; *** : p < .001"
    , align = c("l", rep("r", 6), "l")
    , placement = "hp")

```


### time point 4: 6 - 8 seconds ###

```{r tblAov4, results='asis'}

apa_table(
    aov_sa_dur_4$anova_table %>%
        rownames_to_column(var = "effect") %>%
      rename('p' = `Pr(>F)`) %>% 
      mutate(` ` = case_when(p<0.001 ~ "***",
                             p<0.01  ~ "**",
                             p<0.05 ~ "*",
                             p<0.1 ~ ".",
                             p>=.01 ~ " "),
               effect = case_when(effect == "group_id" ~ "Group",
                                  effect == "fix_id" ~ "ROI",
                                  effect == "group_id:fix_id"~ "Group x ROI")) 
    , caption = "time point 4: 6 - 8 seconds"
    , note = "MSE: mean squared error; ges: generalized eta square; * : p < .05; ** : p < .01; *** : p < .001"
    , align = c("l", rep("r", 6), "l")
    , placement = "hp")

```


### time point 5: 8 - 10 seconds ###

```{r tblAov5, results='asis'}

apa_table(
    aov_sa_dur_5$anova_table %>%
rownames_to_column(var = "effect") %>%
      rename('p' = `Pr(>F)`) %>% 
      mutate(` ` = case_when(p<0.001 ~ "***",
                             p<0.01  ~ "**",
                             p<0.05 ~ "*",
                             p<0.1 ~ ".",
                             p>=.01 ~ " "),
               effect = case_when(effect == "group_id" ~ "Group",
                                  effect == "fix_id" ~ "ROI",
                                  effect == "group_id:fix_id"~ "Group x ROI"))     , caption = "time point 5: 8 - 10 seconds"
    , note = "MSE: mean squared error; ges: generalized eta square; * : p < .05; ** : p < .01; *** : p < .001"
    , align = c("l", rep("r", 6), "l")
    , placement = "hp")

```


## S3 ANOVA including all ROIs  ##

According to our research question we only compared gaze following (cued object
vs. uncued object) **or** social attention (head vs. body) in the accompanying
manuscript. To compare prioritization across gaze following and social attention
effects, an ANOVA with all ROIs can be calculated. This allows for a comparison
between all ROIs. Below are the results of 2 x 4 ANOVAs including Group
(explicit encoding vs. free viewing) and ROI (head, body, object cued, object
uncued). Results indicate that the head ROI was fixated earlier, longer and more
often than any of the other ROIs.


```{r, include=FALSE}

source(path(path_scripts_analysis, "aov_all.R"))

```

### Fixation latency ###

```{r tblAovAllLat, results='asis'}

apa_table(
    aov_all_lat$anova_table %>%
      rownames_to_column(var = "effect") %>%
      rename('p' = `Pr(>F)`) %>% 
      mutate(` ` = case_when(p<0.001 ~ "***",
                             p<0.01  ~ "**",
                             p<0.05 ~ "*",
                             p<0.1 ~ ".",
                             p>=.01 ~ " "),
               effect = case_when(effect == "group_id" ~ "Group",
                                  effect == "fix_id" ~ "ROI",
                                  effect == "group_id:fix_id"~ "Group x ROI"))
    , caption = "Fixation latency"
    , note = "MSE: mean squared error; MSE: mean squared error; ges: generalized eta square; * : p < .05; ** : p < .01; *** : p < .001"
    , align = c("l", rep("r", 6), "l")
    , placement = "hp")

```

&NewLine;
&NewLine;

```{r figAovAllLat, fig.cap = "Fixation latencies as a function of the region of interest and group. Error bars represent 95% confidence interval.", dev.args = list(bg = 'white'), fig.height=3, fig.width= 7.5}

emmip(aov_all_lat, group_id~fix_id, CIs = TRUE) +
  scale_x_discrete(labels = c("head", "body", "cued", "uncued"),
      name = "ROIs") +
  scale_y_continuous(name="Fixation latency (in ms)")

```

### Fixation duration ###

```{r tblAovAllDur, results='asis'}

apa_table(
    aov_all_dur$anova_table %>%
      rownames_to_column(var = "effect") %>%
      rename('p' = `Pr(>F)`) %>% 
      mutate(` ` = case_when(p < 0.001 ~ "***",
                             p < 0.01  ~ "**",
                             p < 0.05 ~ "*",
                             p < 0.1 ~ ".",
                             p >= .01 ~ " "),
               effect = case_when(effect == "group_id" ~ "Group",
                                  effect == "fix_id" ~ "ROI",
                                  effect == "group_id:fix_id"~ "Group x ROI"))
    , caption = "Fixation duration"
    , note = "MSE: mean squared error; MSE: mean squared error; ges: generalized eta square; * : p < .05; ** : p < .01; *** : p < .001"
    , align = c("l", rep("r", 6), "l")
    , placement = "hp")

```

&NewLine;
&NewLine;

```{r figAovAllDur, fig.cap = "Fixation duration as a function of the region of interest and group. Error bars represent 95% confidence interval.", dev.args = list(bg = 'white'), fig.height=3, fig.width= 7.5}

emmip(aov_all_dur, group_id~fix_id, CIs = TRUE) +
  scale_x_discrete(labels = c("head", "body", "cued", "uncued"),
      name = "ROIs") +
  scale_y_continuous(name="Fixation duration (in %)")

```

### Fixation number ###

```{r tblAovAllNum, results='asis'}

apa_table(
    aov_all_num$anova_table %>%
      rownames_to_column(var = "effect") %>%
      rename('p' = `Pr(>F)`) %>% 
      mutate(` ` = case_when(p< 0.001 ~ "***",
                               p<0.01  ~ "**",
                               p<0.05 ~ "*",
                               p<0.1 ~ ".",
                               p>= .01 ~ " "),
               effect = case_when(effect == "group_id" ~ "Group",
                                  effect == "fix_id" ~ "ROI",
                                  effect == "group_id:fix_id"~ "Group x ROI"))
    , caption = "Fixation number"
    , note = "MSE: mean squared error; ges: generalized eta square; * : p < .05; ** : p < .01; *** : p < .001"
    , align = c("l", rep("r", 6), "l")
    , placement = "hp")

```

&NewLine;
&NewLine;

```{r figAovAllNum, fig.cap = "Fixation numbers as a function of the region of interest and group. Error bars represent 95% confidence interval.", dev.args = list(bg = 'white'), fig.height=3, fig.width= 7.5}

emmip(aov_all_num, group_id~fix_id, CIs = TRUE) +
    scale_x_discrete(
      labels = c("head", "body", "cued", "uncued"),
      name = "ROIs") +
  scale_y_continuous(name="Fixation number (in %)")

```
