---
title: "Supplementary Material"
output: bookdown::word_document2

---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo=FALSE, warning = FALSE)

source("../../../../02_scripts/01-libraries.R")
source("../../../../02_scripts/02-paths.R")
theme_set(theme_cowplot())
```

```{r load packages and data}

source(path(path_scripts_data, "eyetracking.R"))
source(path(path_scripts_data, "memory.R"))
source(path(path_scripts_data, "questionnaire.R"))
source(path(path_scripts_data, "rois.R"))

```

# ROIs #

```{r}

source(path(path_scripts_publ, "dscr_roi.R"))

```

## List of all ROIs ##

In our study, each scene contained two central objects. Below is the full list
of all objects presented in the scenes. Note that objects were counter balanced
being cued at and on which side of the image they were presented.

|     stim_id | 1                         | 2                |
| :---------: | :-----------------------: | :--------------: |
|          01 | orange                    | melon            |
|          02 | punches                   | roller stick     |
|          03 | bike helmet               | stethoscope      |
|          04 | rack                      | ventilator       |
|          05 | *blackroll*               | hair dryer       |
|          06 | fruit bowl                | globe            |
|          07 | toaster                   | thermos flask    |
|          08 | marmalade                 | watch            |
|          09 | cup                       | water bottle     |
|          10 | brush                     | glasses          |
|          11 | chair                     | bucket           |
|          12 | binoculars                | camera           |
|          13 | book                      | laptop           |
|          14 | headphones                | folder           |
|          15 | water glass               | towel            |
|          16 | baggage                   | cap              |
|          17 | strawberries              | shoe             |
|          18 | ukulele                   | hand brush       |
|          19 | drum                      | hat              |
|          20 | bowl                      | cushions         |
|          21 | pencil                    | smartphone       |
|          22 | feather                   | elephant         |
|          23 | saw                       | hammer           |
|          24 | flower                    | jug              |
|          25 | coffee grinder            | candle           |
|          26 | bulb                      | flashlight       |

## Descriptives ##

Each scene contained five regions: Background, Head, Body, Cued object, Uncued
object. For a complete overview for average ROI size in pixel, centimeter,
visual degree, total pixel or position on image.

```{r tblSize, results='asis'}

apa_table(
    dscr_roi %>% select(roi_id, ends_with("size")),
    caption = "Sizes of the regions drawn into the stimuli.",
    note = "Mean [m] and its standard deviation [sd] of the number of all pixel of a region [size]"
    , align = c("l", rep("r", 2))
    , placement = "hp")

```



```{r tblCm, results='asis'}

apa_table(
    dscr_roi %>% select(roi_id, ends_with("cm"))
    , caption = "Width and height of the regions drawn into the stimuli."
    , note = "Mean [m] and its standard deviation [sd] of the width [w] and height [h] of the regions in centimeters [cm]"
    , align = c("l", rep("r", 4))
    , placement = "hp")

```



```{r tblDg, results='asis'}

apa_table(
    dscr_roi %>% select(roi_id, ends_with("dg"))
    , caption = "Width and height of the regions drawn into the stimuli."
    , note = "Mean [m] and its standard deviation [sd] of the width [w] and height [h] of the regions in visual degree [dg]."
    , align = c("l", rep("r", 4))
    , placement = "hp")

```



```{r tblPx, results='asis'}

apa_table(
    dscr_roi %>% select(roi_id, ends_with("px"))
    , caption = "Width and height of the regions drawn into the stimuli."
    , note = "Mean [m] and its standard deviation [sd] of the width [w] and height [h] of the regions in pixels [px]."
    , align = c("l", rep("r", 4))
    , placement = "hp")

```



```{r tblXy, results='asis'}

apa_table(
    dscr_roi %>% select(roi_id, ends_with("_x"), ends_with("_y"))
    , caption = "Positions of the regions drawn into the stimuli."
    , note = "Mean [m] and its standard deviation [sd] of the position [x] and [y] of the regions in the image."
    , align = c("l", rep("r", 2))     
    , placement = "hp")

```

Distances between the head, the cued and the uncued objects.

```{r tblDist, results='asis'}

apa_table(
    dscr_roi_dist
    , caption = "Distance between objects (cued & uncued) and head."
    , note = "Mean [m] and its standard deviation [sd] of the position [x] and [y] of the regions in the image."
    , align = c("l", rep("r", 6))     
    , placement = "hp")

```



# S2 Follow-up ANOVAs on social attention #

In our main analysis the the three-way interaction ROI x Group x Time was
significant. As follow-up test separate ANOVAs for each time point were 
performed to reveal time specific patterns. Only the first ANOVA is reported in
the manuscript with all relevant details due to its significance. 
Below are all ANOVA tables for each time point.

```{r, include=FALSE}

source(path(path_scripts_publ, "aov_sa.R"))

```


## time point 1: 0 - 2 seconds ##

```{r tblAov1, results='asis'}

apa_table(
    aov_sa_dur_1$anova_table %>%
        rownames_to_column(var = "effect") %>% 
        mutate(` ` = case_when(`Pr(>F)`< 0.001 ~ "***",
                               `Pr(>F)`<0.01  ~ "**",
                               `Pr(>F)`<0.05 ~ "*",
                               `Pr(>F)`<0.1 ~ ".",
                               `Pr(>F)`>= .01 ~ " "))
    , caption = "time point 1: 0 - 2 seconds"
    , note = "MSE: mean squared error; ges: generalized eta square; * : p < .05; ** : p < .01; *** : p < .001"
    , align = c("l", rep("r", 6), "l")     
    , placement = "hp")

```


## time point 2: 2 - 4 seconds ##

```{r tblAov2, results='asis'}

apa_table(
    aov_sa_dur_2$anova_table %>%
        rownames_to_column(var = "effect") %>% 
        mutate(` ` = case_when(`Pr(>F)`< 0.001 ~ "***",
                               `Pr(>F)`<0.01  ~ "**",
                               `Pr(>F)`<0.05 ~ "*",
                               `Pr(>F)`<0.1 ~ ".",
                               `Pr(>F)`>= .01 ~ " "))
    , caption = "time point 2: 2 - 4 seconds"
    , note = "MSE: mean squared error; ges: generalized eta square; * : p < .05; ** : p < .01; *** : p < .001"
    , align = c("l", rep("r", 6), "l")     
    , placement = "hp")

```


## time point 3: 4 - 6 seconds ##

```{r tblAov3, results='asis'}

apa_table(
    aov_sa_dur_3$anova_table %>%
        rownames_to_column(var = "effect") %>% 
        mutate(` ` = case_when(`Pr(>F)`< 0.001 ~ "***",
                               `Pr(>F)`<0.01  ~ "**",
                               `Pr(>F)`<0.05 ~ "*",
                               `Pr(>F)`<0.1 ~ ".",
                               `Pr(>F)`>= .01 ~ " "))
    , caption = "time point 3: 4 - 6 seconds"
    , note = "MSE: mean squared error; ges: generalized eta square; * : p < .05; ** : p < .01; *** : p < .001"
    , align = c("l", rep("r", 6), "l")     
    , placement = "hp")

```


## time point 4: 6 - 8 seconds ##

```{r tblAov4, results='asis'}

apa_table(
    aov_sa_dur_4$anova_table %>%
        rownames_to_column(var = "effect") %>% 
        mutate(` ` = case_when(`Pr(>F)`< 0.001 ~ "***",
                               `Pr(>F)`<0.01  ~ "**",
                               `Pr(>F)`<0.05 ~ "*",
                               `Pr(>F)`<0.1 ~ ".",
                               `Pr(>F)`>= .01 ~ " "))
    , caption = "time point 4: 6 - 8 seconds"
    , note = "MSE: mean squared error; ges: generalized eta square; * : p < .05; ** : p < .01; *** : p < .001"
    , align = c("l", rep("r", 6), "l")     
    , placement = "hp")

```


## time point 5: 8 - 10 seconds ##

```{r tblAov5, results='asis'}

apa_table(
    aov_sa_dur_5$anova_table %>%
        rownames_to_column(var = "effect") %>% 
        mutate(` ` = case_when(`Pr(>F)`< 0.001 ~ "***",
                               `Pr(>F)`<0.01  ~ "**",
                               `Pr(>F)`<0.05 ~ "*",
                               `Pr(>F)`<0.1 ~ ".",
                               `Pr(>F)`>= .01 ~ " "))
    , caption = "time point 5: 8 - 10 seconds"
    , note = "MSE: mean squared error; ges: generalized eta square; * : p < .05; ** : p < .01; *** : p < .001"
    , align = c("l", rep("r", 6), "l")     
    , placement = "hp")

```


# S3 All ROIs ANOVA #

According to our research question we only compare gaze following (cued object vs uncued object)
**or** social attention (head vs body) in the accompanying manuscript. 
To compare prioritization across gaze following and social attention effects,
an ANOVA with all ROIs can be calculated. This allows for a comparison between all ROIs.
Below are the results for these 4 ROIs (head, body, object cued, object uncued)
x 2 Groups (explicit encoding vs free viewing) ANOVAs.



```{r, include=FALSE}

source(path(path_scripts_publ, "aov_all.R"))

```

## Fixation latency ##

```{r tblAovAllLat, results='asis'}

apa_table(
    aov_all_lat$anova_table %>%
        rownames_to_column(var = "effect") %>% 
        mutate(` ` = case_when(`Pr(>F)`< 0.001 ~ "***",
                               `Pr(>F)`<0.01  ~ "**",
                               `Pr(>F)`<0.05 ~ "*",
                               `Pr(>F)`<0.1 ~ ".",
                               `Pr(>F)`>= .01 ~ " "))
    , caption = "Fixation latency"
    , note = "MSE: mean squared error; MSE: mean squared error; ges: generalized eta square; * : p < .05; ** : p < .01; *** : p < .001"
    , align = c("l", rep("r", 6), "l")     
    , placement = "hp")

```


```{r figAovAllLat, fig.cap = "Fixation latencies as a function of the region of interest and group. Error bars represent 95% confidence intervall.", dev.args = list(bg = 'white'), fig.height=3, fig.width= 7.5}

emmip(aov_all_lat, group_id~fix_id, CIs = TRUE) +
  scale_x_discrete(labels = c("cued", "head", "body", "uncued"))

```


## Fixation duration ##

```{r tblAovAllDur, results='asis'}

apa_table(
    aov_all_dur$anova_table %>%
        rownames_to_column(var = "effect") %>% 
        mutate(` ` = case_when(`Pr(>F)`< 0.001 ~ "***",
                               `Pr(>F)`<0.01  ~ "**",
                               `Pr(>F)`<0.05 ~ "*",
                               `Pr(>F)`<0.1 ~ ".",
                               `Pr(>F)`>= .01 ~ " "))
    , caption = "Fixation duration"
    , note = "MSE: mean squared error; MSE: mean squared error; ges: generalized eta square; * : p < .05; ** : p < .01; *** : p < .001"
    , align = c("l", rep("r", 6), "l")     
    , placement = "hp")

```


```{r figAovAllDur, fig.cap = "Fixation duration as a function of the region of interest and group. Error bars represent 95% confidence intervall.", dev.args = list(bg = 'white'), fig.height=3, fig.width= 7.5}

emmip(aov_all_dur, group_id~fix_id, CIs = TRUE) +
  scale_x_discrete(labels = c("cued", "head", "body", "uncued"))

```


## Fixation number ##

```{r tblAovAllNum, results='asis'}

apa_table(
    aov_all_num$anova_table %>%
        rownames_to_column(var = "effect") %>% 
        mutate(` ` = case_when(`Pr(>F)`< 0.001 ~ "***",
                               `Pr(>F)`<0.01  ~ "**",
                               `Pr(>F)`<0.05 ~ "*",
                               `Pr(>F)`<0.1 ~ ".",
                               `Pr(>F)`>= .01 ~ " "))
    , caption = "Fixation number"
    , note = "MSE: mean squared error; ges: generalized eta square; * : p < .05; ** : p < .01; *** : p < .001"
    , align = c("l", rep("r", 6), "l")     
    , placement = "hp")

```


```{r figAovAllNum, fig.cap = "Fixation numbers as a function of the region of interest and group. Error bars represent 95% confidence intervall.", dev.args = list(bg = 'white'), fig.height=3, fig.width= 7.5}

emmip(aov_all_num, group_id~fix_id, CIs = TRUE) +
    scale_x_discrete(labels = c("cued", "head", "body", "uncued"))

```


