---
title: "Presence of persons in naturalistic scenes and consequences - A conceptual replication"
subtitle: "Poster for the Interactive Eye Gaze Conference, London 2018"
output: html_notebook
---

```{r Descriptives fixations joint, include=FALSE}

# Descriptives for fixation chacracteristics for joint attention

dscr.fixjoi <- df.w.et %>% summarise(mean(fix.gaze), sd(fix.gaze), mean(fix.nongaze), sd(fix.nongaze), mean(fixn.gaze), sd(fixn.gaze), mean(fixn.nongaze), sd(fixn.nongaze), mean(fixlat.gaze), mean(fixlat.nongaze), sd(fixlat.nongaze))

dscr.fixjoi.group <- df.w.et %>% group_by(group) %>% summarise(mean(fix.gaze), sd(fix.gaze), mean(fix.nongaze), sd(fix.nongaze), mean(fixn.gaze), sd(fixn.gaze), mean(fixn.nongaze), sd(fixn.nongaze), mean(fixlat.gaze), sd(fixlat.gaze), mean(fixlat.nongaze), sd(fixlat.nongaze))

```

```{r descriptives saccade, include=FALSE}
# dscr.sac <- df.w.et %>% summarise(m_sac.pgaze = mean(sac.pgaze), sd_sac.pgaze = sd(sac.pgaze),
#                                   m_sac.pnongaze=mean(sac.pnongaze), sd_sac.pnongaze=sd(sac.pnongaze),
#                                   m_sac.fgaze=mean(sac.fgaze), sd_sac.fgaze=sd(sac.fgaze),
#                                   m_sac.fnongaze=mean(sac.fnongaze), sd_sac.fnongaze=sd(sac.fnongaze),
#                                   m_sac.bgaze=mean(sac.bgaze), sd_sac.bgaze=sd(sac.bgaze),
#                                   m_sac.bnongaze=mean(sac.bnongaze), sd_sac.bnongaze=sd(sac.bnongaze))

# old
# dscr.sac.rpl <- df.w.et %>%
#   group_by(group) %>%
#   summarise_at(vars(sac.pgaze:sac.bnongaze), funs(mean,sd,se=sd(.)/sqrt(n()))) %>% # mit den funs() die variablen vars(von:bis) berechnen
#   gather(key, measure, sac.pgaze_mean:sac.bnongaze_se) %>% # ins longformat
#   mutate(stat = as.factor(map(strsplit(key,"[[:punct:]]"), ~.x[3]) %>% unlist()),
#          area = map(strsplit(key,"[[:punct:]]"), ~.x[2]) %>% unlist(),
#          area = as.factor(substring(area,1,1)),
#          gazed = map(strsplit(key,"[[:punct:]]"), ~.x[2]) %>% unlist(),
#          gazed = as.factor(substring(gazed,2)),
#          key = as.factor("replication")) %>% #rausnehmen, zur kontrolle, ob alles passt, was oben l채uft.
#   select(-measure, everything()) %>% # neusortieren der variablen
#   select(key, everything())
# 
# dscr.sac.zwckl <- data.frame(key=c("zwickel","zwickel"), group=c("free", "free"), stat=c("mean", "se"), area=(c("f")), gazed=c("gaze", "gaze", "nongaze", "nongaze"), measure=c(.14,0.01,.09,0.01)) # free = person
# 
# dscr.sac <- rbind(dscr.sac.rpl, dscr.sac.zwckl)

dscr.sac <- df.w.et %>%
  group_by(group) %>%
  summarise_at(vars(sac.pgaze:sac.bnongaze), funs(mean,sd,se=sd(.)/sqrt(n()))) %>% # mit den funs() die variablen vars(von:bis) berechnen
  gather(key, measure, sac.pgaze_mean:sac.bnongaze_se) %>% # ins longformat
  mutate(stat = as.factor(map(strsplit(key,"[[:punct:]]"), ~.x[3]) %>% unlist()),
         area = map(strsplit(key,"[[:punct:]]"), ~.x[2]) %>% unlist(),
         area = as.factor(substring(area,1,1)),
         gazed = map(strsplit(key,"[[:punct:]]"), ~.x[2]) %>% unlist(),
         gazed = as.factor(substring(gazed,2)),
         key = as.factor("replication")) %>% #rausnehmen, zur kontrolle, ob alles passt, was oben l채uft.
  select(-measure, everything()) %>% # neusortieren der variablen
  select(key, everything()) %>%
  rbind(., data.frame(key=c("zwickel"), group=c("free"), stat=c("mean", "se"), area=(c("f")), gazed=c("gaze", "gaze", "nongaze", "nongaze"), measure=c(.14,0.01,.09,0.01))) # hinzuf체gen der Daten aus Zwickel2010 free = person


```

```{r descriptives fix*, include=FALSE}
# dscr.sac <- df.w.et %>% summarise(m_sac.pgaze = mean(sac.pgaze), sd_sac.pgaze = sd(sac.pgaze),
#                                   m_sac.pnongaze=mean(sac.pnongaze), sd_sac.pnongaze=sd(sac.pnongaze),
#                                   m_sac.fgaze=mean(sac.fgaze), sd_sac.fgaze=sd(sac.fgaze),
#                                   m_sac.fnongaze=mean(sac.fnongaze), sd_sac.fnongaze=sd(sac.fnongaze),
#                                   m_sac.bgaze=mean(sac.bgaze), sd_sac.bgaze=sd(sac.bgaze),
#                                   m_sac.bnongaze=mean(sac.bnongaze), sd_sac.bnongaze=sd(sac.bnongaze))

# dscr.fix.rpl <- df.w.et %>%
#   group_by(group) %>%
#   summarise_at(vars(fix.face:fixlat.nongaze), funs(mean,sd,se=sd(.)/sqrt(n()))) %>% # mit den funs() die variablen vars(von:bis) berechnen
#   gather(key, measure, fix.face_mean:fixlat.nongaze_se) %>% # ins longformat
#   mutate(fix = as.factor(map(strsplit(key,"[[:punct:]]"), ~.x[1]) %>% unlist()),
#          gazed = map(strsplit(key,"[[:punct:]]"), ~.x[2]) %>% unlist(),
#          gazed = factor(substring(gazed,1), levels=c("face", "body", "gaze", "nongaze")),
#          stat = as.factor(map(strsplit(key,"[[:punct:]]"), ~.x[3]) %>% unlist()),
#          key = as.factor("replication")) %>%
#   select(-measure, everything()) %>% # neusortieren der variablen
#   select(key, everything())
# 
# dscr.fix.zwckl <- data.frame(key="zwickel", group="free", fix = c("fix", "fix", "fix", "fix", "fixn", "fixn", "fixn", "fixn", "fixlat", "fixlat", "fixlat", "fixlat"), gazed = c("gaze","gaze", "nongaze", "nongaze"), stat = c("mean", "se"), measure = c(0.08, .01, .07, .01, 5.89, .37, 5.24, .34, 3588, 133, 4008, 166)) # free = person

dscr.fix <- df.w.et %>%
  group_by(group) %>%
  summarise_at(vars(fix.face:fixlat.nongaze), funs(mean,sd,se=sd(.)/sqrt(n()))) %>% # mit den funs() die variablen vars(von:bis) berechnen
  gather(key, measure, fix.face_mean:fixlat.nongaze_se) %>% # ins longformat
  mutate(fix = as.factor(map(strsplit(key,"[[:punct:]]"), ~.x[1]) %>% unlist()),
         gazed = map(strsplit(key,"[[:punct:]]"), ~.x[2]) %>% unlist(),
         gazed = factor(substring(gazed,1), levels=c("face", "body", "gaze", "nongaze")),
         stat = as.factor(map(strsplit(key,"[[:punct:]]"), ~.x[3]) %>% unlist()),
         key = as.factor("replication")) %>% 
  select(-measure, everything()) %>% # neusortieren der variablen
  select(key, everything()) %>% rbind(., data.frame(key="zwickel", group="free",fix=c("fix","fix","fix","fix","fixn","fixn","fixn","fixn","fixlat","fixlat","fixlat","fixlat"), gazed=c("gaze","gaze", "nongaze", "nongaze"), stat=c("mean","se"), measure=c(0.08,.01,.07,.01,5.89,.37,5.24,.34,3588,133,4008,166)))  #hinzuf체gen der repl. data # free = person

```

<!-- VERGLEICH -->
```{r Prerequisits}

# Library
library("tidyverse")
library("ggsignif")
library("scales")
library("extrafont")

# Design variables
customColors = c("#0072B2", "#F0E442")
customTheme = theme(text=element_text(size=24, family="Candara"))
customLabels = c("Objects gazed-at", " Objects not gazed-at")
customLabels = element_blank()

```

```{r Boxplot fixation latency}

boxplot.fixlat.gaze <- df.l.et %>% filter(key == "fixlat.gaze" | key == "fixlat.nongaze") %>% 
  ggplot(aes(x = group, y = value, fill = region)) +
  geom_boxplot(position = "dodge") +
  geom_signif(annotation="***", y_position=5800, xmin=1, xmax=2, tip_length = 0.0, vjust = 0.5) +
  geom_signif(annotation="***", y_position=5600, xmin=.81, xmax=1.188, tip_length = 0.0, vjust = 0.5) +
  geom_signif(annotation="*", y_position=5600, xmin=1.81, xmax=2.188, tip_length = 0.0, vjust = 0.5) +
  geom_signif(annotation="**", y_position=5400, xmin=.81, xmax=1.81, tip_length = 0.0, vjust = 0.5) +
  geom_signif(annotation="*", y_position=5200, xmin=1.188, xmax=2.188, tip_length = 0.0, vjust = 0.5) +
  scale_y_continuous(name = "Fixation latency (in ms)") +
  scale_x_discrete(name = "Groups", labels=c("free encoding", "explicit encoding")) +
  scale_fill_manual(name = element_blank(), guide=FALSE, values=customColors) +
  theme_minimal() +
  customTheme #+
  ggsave("bplt.lixlat.png")

boxplot.fixlat.gaze

```


```{r Boxplot fixation duration}


boxplot.fix.gaze <- df.l.et %>% filter(key == "fix.gaze" | key == "fix.nongaze") %>% 
  ggplot(aes(x = group, y=value, fill = region)) +
  geom_boxplot(position = "dodge") +
  geom_signif(annotation="***", y_position=.38, xmin=1.188, xmax=2.188, tip_length = 0.0, vjust = 0.5) +
  #geom_signif(annotation="***", y_position=.36, xmin=1.188, xmax=1.81, tip_length = 0.0, vjust = 0.5) +
  #geom_signif(annotation="*", y_position=.42, xmin=0.81, xmax=2.188, tip_length = 0.0, vjust = 0.5) +
  geom_signif(annotation="*", y_position=.36, xmin=0.81, xmax=1.81, tip_length = 0.0, vjust = 0.5) +
  geom_signif(annotation="*", y_position=.36, xmin=0.81, xmax=1.81, tip_length = 0.0, vjust = 0.5) +
  scale_y_continuous(name = "relative Fixation duration", labels = percent_format()) +
  scale_x_discrete(name = "Groups", labels=c("free encoding", "explicit encoding")) +
  scale_fill_manual(name = element_blank(), guide=FALSE, values=customColors)+
  theme_minimal() +
  customTheme +
  ggsave("bplt.fixdur.png")

boxplot.fix.gaze
```


```{r Boxplot saccades head-obkject}
boxplot.sac <- df.l.et %>% filter(key == "sac.fgaze" | key == "sac.fnongaze") %>% 
  ggplot(aes(x = group, y=value, fill = key)) +
  geom_boxplot(position = "dodge") +
  geom_signif(annotation="*", y_position=.265, xmin=.84, xmax=1.16, tip_length = 0.01, vjust = 0.5) +
  geom_signif(annotation="*", y_position=.28, xmin=1, xmax=2, tip_length = 0.01, vjust = 0.5) +
  geom_signif(annotation="*", y_position=.265, xmin=1.84, xmax=2.16, tip_length = 0.01, vjust = 0.5)+
  scale_y_continuous(name = "Saccades leaving the head", labels = percent_format()) +
  scale_x_discrete(name = "Groups", labels=c("free encoding", "explicit encoding")) +
scale_fill_manual(name = element_blank(), guide=FALSE, values=customColors) +
  theme_minimal() +
  customTheme +
  ggsave("bplt.sacho.png")

boxplot.sac
```

# Introduction

Humans in their social environment rely on the information conspecifics provide. One important signal in social communication is eye gaze. The current study (n=90) sought to replicate and extend previous findings of attentional guidance by eye gaze in complex everyday scenes and to investigate how robust this prioritization is against top-down modulation, half of the observers receive a memory task that required scanning the whole scene instead of exclusively focusing on *referenced* objects.


# Methods

# Results
<!-- Drei Plots: Latenz, Duration & Sakkaden: Kopf-Objekt -->

# Discussion

# References

